Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2025-02-25 main.tex
improving figures v2. WIP
last figure
some small explanations of experiments added

\begin{figure}[tb]
  \centering
  \includegraphics[width=1.08\columnwidth] {images/success-rates-large2}
  \vspace{-0.8cm}
  \caption{Success rates on the default cluster. Higher is better.}
  \label{fig:success-rates-large}
  \vspace{-0.15cm}
\end{figure}

@@

Similarly to the default cluster, we observe that the makespan of \heftmm is usually higher
than with \heft (see Fig.~\ref{fig:ms-relations-by-workflow-constrained}), but the \heft schedules are
almost all invalid. It is thus worthwhile to resort to \heftmm for large workflows
in a constrained cluster, since tasks are processed in an order that minimizes
the memory usage of schedule.
%
%    The makespans it produces are larger, but it seems to order the vertices in a similar way on both the small and the large workflows,
%    rather than resorting to more memory-consuming ordering that other heuristics and the baseline produces.
%    This makes it especially valuable for very large workflows in situations of very constrained memory in the cluster.
%
%

Memory usages on the constrained cluster are depicted in~Fig.~\ref{fig:memory-usage-constrained},
and we observe that the memory footprint of \heftmm remains constant with workflow size.

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=0.95\columnwidth] {images/UpdatesMss2}
    \caption{Relative (excess) makespan of \heftbl, \heftblc and \heftmm. Smaller is better.}
    \label{fig:updates-ms}
    \vspace{-0.3cm}
\end{figure}

>>>>

\begin{figure}[tb]
  \centering
  \includegraphics[width=1.08\columnwidth] {images/success-rates-large2}
  \vspace{-0.8cm}
  \caption{Success rates \new{by workflow size and algorithm} on the default cluster. Higher is better.}
  \label{fig:success-rates-large}
  \vspace{-0.15cm}
\end{figure}

@@

Similarly to the default cluster, we observe that the makespan of \heftmm is usually higher
than with \heft (see Fig.~\ref{fig:ms-relations-by-workflow-constrained}), but the \heft schedules are
almost all invalid. It is thus worthwhile to resort to \heftmm for large workflows
in a constrained cluster, since tasks are processed in an order that minimizes
the memory usage of schedule.
\new{Due to a varying nature of the workflow generator, some larger workflows can have smaller makespans than their
smaller counterparts due to more parallel execution due to higher fanout or other factors of the workflow's
internal composition.
}

%
%    The makespans it produces are larger, but it seems to order the vertices in a similar way on both the small and the large workflows,
%    rather than resorting to more memory-consuming ordering that other heuristics and the baseline produces.
%    This makes it especially valuable for very large workflows in situations of very constrained memory in the cluster.
%
%

Memory usages on the constrained cluster are depicted in~Fig.~\ref{fig:memory-usage-constrained}.
\new{We plot the average memory usage in the cluster per algorithm and workflow size},
and we observe that the memory footprint of \heftmm remains constant with workflow size.

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=0.95\columnwidth] {images/UpdatesMss2}
    \caption{Relative (excess) makespan of \heftbl, \heftblc and \heftmm \new{in case of no recomputation}. Smaller is better.}
    \label{fig:updates-ms}
    \vspace{-0.3cm}
\end{figure}
